Query Optimization for Dynamic Imputation

### 2017-05-15 paper/examples.tex
paper: rewording

\review{
As an alternative strategy, the analyst can start by executing her query with $\alpha=1$ and
incrementally reducing $\alpha$, as long as execution of the query completes within some
acceptable time bound.
\ProjectName{}'s planning algorithm can expose the final set of plans with optimal
time-quality trade-offs, which allows the user to adjust her choice of $\alpha$ to select from these plans.
}

>>>>

\review{
As an alternative strategy, the analyst can start by executing her query with $\alpha=1$ and
incrementally reducing $\alpha$, as long as execution of the query completes acceptably quickly.
\ProjectName{}'s planning algorithm can also produce a set of plans with optimal
time-quality trade-offs, which allows the user to adjust her choice of $\alpha$ to select from these plans.
}
